---
title: "Product Analyst Task"
author: "Faith Kemunto"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r include=FALSE}
library(odbc)
library(DBI)
library(dbplyr)
library(RPostgres)
library(tidyverse)
library(dplyr)
library(tibble)
library(lubridate)
library(lsr)
library(ggplot2)
library(forcats)
library(plotly)
```
1. Connect to PostgreSQL to import the tables created into R.

```{r, include=TRUE}
con <- DBI::dbConnect(RPostgres::Postgres(),dbname = "wefarmtestdb",user = rstudioapi::askForPassword("Database user"),password = rstudioapi::askForPassword("Database password"),port = "5432")
```


2. View the list of tables

```{r, include=TRUE}
dbListTables(con)

```

3. Finding the click through value.

```{sql connection=con, output.var="click_through_value"}
SELECT
	Content,
	impression.keyword,
	COUNT(*) AS click_through_value
FROM
	target_group
INNER JOIN impression
	ON target_group.keyword = impression.keyword
GROUP BY content,impression.keyword
ORDER BY impression.keyword;
```
```{r}
print(click_through_value)
```

4. Finding the join value

```{sql connection=con, output.var="join_value"}
SELECT
	target_group_id,
	COUNT (*) AS join_value
FROM target_group_user
INNER JOIN member
	ON user_phone_number = member_phone_number
WHERE target_group_id 
	IN(1,3,5,6)
GROUP BY target_group_id;
```
```{r, include=TRUE}
print(join_value)
```

5. Finding the contribution value

```{sql connection=con, output.var="contribution_value"}
SELECT 
	target_group_id,
	COUNT(*) AS contribution_value
FROM member_post
INNER JOIN target_group_user
	ON member_post.member_phone_number = target_group_user.user_phone_number
WHERE target_group_id
	IN(1,3,5,6)
GROUP BY target_group_id;
```
```{r, include=TRUE}
print(contribution_value)

```
6. Finding the Click Through Rate

```{sql connection=con, output.var="target_group_user"}
SELECT
	target_group_id,
	COUNT (*) AS target_number
FROM target_group_user
WHERE target_group_id
	IN(1,3,5,6)
GROUP BY target_group_id
ORDER BY target_group_id;
```
```{r, include=TRUE}
click_through_df <- rbind("Target number" =target_group_user$target_number,"Click value"=click_through_value$click_through_value,"Join value" =join_value$join_value)
colnames(click_through_df) <- c("Variation 1", "Variation 3" , "Variation 5", "Variation 6")
click_through_rate <- mapply('/', click_through_df[2,],click_through_df[1,])*100
click_through_rate

```

7. Finding the join rate

```{r, include=TRUE}
join_rate <- mapply('/', click_through_df[3,],click_through_df[2,])*100
join_rate

```

8. Plotting the join rate and click rate

```{r, include=TRUE}
click_join_df <- as.data.frame(t(rbind (click_through_rate, join_rate)))
click_join_df <- rownames_to_column(click_join_df, var="Variation") %>% head
click_join_df_long <- gather(click_join_df, key="Measure", value="Value", c("click_through_rate", "join_rate"))
plot1 <- click_join_df_long %>%
  arrange(Value) %>%
  mutate(Variation=factor(Variation, levels=rev(unique(Variation)), ordered=TRUE)) %>%
  ggplot( aes(fill=Measure, x=Variation, y=Value))+
  geom_bar(position = "dodge", stat = "identity", width=0.4) +
  ggtitle("Click Through Rate vs Join Rate")+
  xlab("Test Group")+
  ylab("Rate")
ggplotly(plot1)
```
From the plot, we see that variation 5 (2.1985) has a better click through rate than variation 1 (1.86667). We also see that variation 1 (32.143) has the best join rate from the sample.

Next we are going to test the null hypothesis i.e the generic message (variation 1) would have had a lower click through rate and join rate than the user-based value propositions (other variations in the test), then further test for the statistical significance of the result.

```{r, include=TRUE}
chisq.test(click_join_df$join_rate,click_join_df$click_through_rate)
```
A chi-squared test statistic at 95% confidence level returns p-values for both click rate and join rate that are greater than 0.05 (i.e 0.2133 > 0.05). This indicates that there isn't enough evidence to to reject the null hypothesis thus we fail to reject the null hypothesis and conclude that the test result is not statistically significant at this point.











